Null Window Correction

### 2020-06-17 output_scripts/Null_Windows.Rmd
adjust color scheme for PR matrices to be red blue

library(compete)
#library(RColorBrewer)
#library(Hmisc)
#library(wCorr)
#library(tidyverse)
library(dplyr)
#library(R.utils)
#library(fields)

@@

## Predictions

For a single cohort now.

```{r}
current_cohort <- 1
load(paste(data_path,cohort_names[current_cohort],
                  "/predict_simulation_",cohort_names[current_cohort],
                  ".RData",sep=''))
```

>>>>

library(compete)
library(RColorBrewer)
#library(Hmisc)
#library(wCorr)
#library(tidyverse)
library(dplyr)
#library(R.utils)
#library(fields)

@@
